TBD

### 2016-09-12 paper/paper.tex
include the experimental evaluation section

\noindent which makes the system unstable in closed-loop using series loop configuration.

@@

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node {Counter-ex} ([yshift=-2em]synth.east)
    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis. \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Works}

>>>>

\noindent which makes the system unstable in closed-loop using the typical series loop configuration.

@@

   \path
    ([yshift=2em]synth.east) edge node {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node {Counter-ex} ([yshift=-2em]synth.east)
    ([xshift=5em]verif.south) edge node {Candidate $P$} ([xshift=5em]bmc.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);
 \end{tikzpicture}
}
 \caption{Counterexample-Guided Inductive Synthesis. \label{fig:CEGIS}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Evaluation}

This section is split into three parts. Section~\ref{experimental-objectives} describes the experimental objectives, while Section~\ref{experimental-setup} discusses the experimental setup and the employed benchmarks. Section~\ref{experimental-results} describes the experimental results related to the application of CEGIS to standard control system benchmarks extracted from the literature.

%---------------------------------
\subsection{Objectives}
\label{experimental-objectives}
%---------------------------------

%---------------------------------
\subsection{Setup}
\label{experimental-setup}
%---------------------------------

%---------------------------------
\subsection{Results}
\label{experimental-results}
%---------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
